### 2018-12-28 Sections/QTCP_protocol_stack.tex
Formatting update

Note that while one can always measure classical data without disturbance, this is not the case with quantum data, where measurements cause wavefunction collapse. Thus, while Alice is always able to know $\hat\rho_\mathrm{classical}$ and $\hat\rho_\mathrm{header}$, she may or may not know $\hat\rho_\mathrm{quantum}$. Clearly if she prepared the state herself, she would (hopefully) know what she was doing. But in general, quantum networks could be used for far less trivial networking, where Alice is, for example, an intermediary in a distributed quantum computation. In this instance, Alice is unlikely to know what her \textsc{Quantum Data} is.

>>>>

Note that while one can always measure classical data without disturbance, this is not the case with quantum data, where measurements cause wave-function collapse. Thus, while Alice is always able to know $\hat\rho_\mathrm{classical}$ and $\hat\rho_\mathrm{header}$, she may or may not know $\hat\rho_\mathrm{quantum}$. Clearly if she prepared the state herself, she would (hopefully) know what she was doing. But in general, quantum networks could be used for far less trivial networking, where Alice is, for example, an intermediary in a distributed quantum computation. In this instance, Alice is unlikely to know what her \textsc{Quantum Data} is.

### 2018-12-28 Sections/about_the_authors.tex
Editing SOTA.
Formatting update

Peter Rohde is an ARC Future Fellow in the Centre for Quantum Software \& Information at the University of Technology Sydney, Australia (UTS:Q$|$SI$\rangle$), and associate member of the Hearne Institute for Theoretical Physics at Louisiana State University. He obtained a Bachelor of Computer Systems Engineering with First Class Honours, and a PhD in theoretical physics at the University of Queensland. He has worked at highly-acclaimed international institutes, including the University of Oxford, University of Queensland, Institute for Molecular Biosciences and Max-Planck Institute for the Science of Light, with over 60 publications and 1,500+ citations in quantum optics, quantum computing, quantum information theory, ecology, and politics. His theoretical proposals have inspired several world-leading experimental efforts, including time-bin encoded \textsc{BosonSampling} and sub-shot-noise limited quantum metrology. In his spare time he is a musician, composer, public speaker, libertarian political activist, charity worker, mountaineer and adrenaline junkie. He regularly speaks at prominent political and scientific outreach events, features in newspaper and magazine articles, and conducts radio interviews. He is a very naughty boy and was expelled from preschool\index{Montessori}.

@@

He-Liang Huang is a Postdoctoral Fellow at the University of Science \& Technology China (USTC). His research interests include secure cloud quantum computing, quantum big data analysis, and the physical implementation of quantum computing architectures, in particular using linear optical and superconducting systems. As an experimentalist he has been a part of several groundbreaking experimental efforts, most notably in the demonstration of world-leading multi-photon optical quantum information processing protocols.

@@

Zu-En Su is a PhD candidate at the University of Science \& Technology China.

@@

Zixin Huang completed her PhD in physics at the University of Sydney, Australia. She is currently a postdoctoral fellow at the University of Sheffield, UK.

@@

Chandrashekar Radhakrishnan is a Postdoctoral Fellow and Bright Overseas Global Corporation Scholar at New York University, Shanghai, Chibna. He is a recipient of the National Natural Science Foundation of China, International Young Scientist research grant. Before Joining NYU Shanghai he worked as a Postdoctoral Fellow at the Institute of Mathematical Science, India and the National Chung Hsing University, Taiwan. He obtained his Master of Science in Physics from the Indian Institute of Technology Madras and a PhD in theoretical physics from University of Madras. He has worked on a variety of fields, including statistical mechanics, mathematical physics and quantum information theory. His fundamental interest in quantum information theory lies in investigating quantum resources alternative to entanglement, which can be used for quantum communication and quantum computation. He has active collaborations with experimentalists, through which he tries to verify his theoretical results. He also has some interest in the application of statistical mechanics to biological problems.

@@

\comment{Simon Devitt}

@@

Si-Hui Tan is a Research Scientist at the Singapore University of Technology \& Design. She obtained a Bachelor of Science with Honours from Caltech, and subsequently a PhD from MIT. She has received numerous awards, including the MIT Presidential Fellowship.

@@

Nana Liu is a Postdoctoral Research Fellow at the Singapore University of Technology \& Design.

@@

Rohit Ramakrishnan is a researcher at the Indian Institute of Science.

@@

Jon Dowling is Professor and Hearne Chair of Theoretical Physics, and Co-Director of the Hearne Institute for Theoretical Physics at Louisiana State University. He has a highly-acclaimed research career, with over 450 publications and 15,000 citations. He is author of the popular book \textit{Schr\"odinger's Killer App: Race to Build the World's First Quantum Computer}.

@@

Tim Byrnes....

@@

Bill Munro obtained his PhD at the University of Waikato, and has since held numerous prestigious fellowships and positions. He is currently Senior Research Scientist and leader of the theoretical quantum physics research group at NTT Japan.

>>>>

\dropcap{P}{eter Rohde} is an ARC Future Fellow in the Centre for Quantum Software \& Information at the University of Technology Sydney, Australia (UTS:Q$|$SI$\rangle$), and associate member of the Hearne Institute for Theoretical Physics at Louisiana State University. He obtained a Bachelor of Computer Systems Engineering with First Class Honours, and a PhD in theoretical physics at the University of Queensland. He has worked at highly-acclaimed international institutes, including the University of Oxford, University of Queensland, Institute for Molecular Biosciences and Max-Planck Institute for the Science of Light, with over 60 publications and 1,500+ citations in quantum optics, quantum computing, quantum information theory, ecology, and politics. His theoretical proposals have inspired several world-leading experimental efforts, including time-bin encoded \textsc{BosonSampling} and sub-shot-noise limited quantum metrology. In his spare time he is a musician, composer, public speaker, libertarian political activist, charity worker, mountaineer and adrenaline junkie. He regularly speaks at prominent political and scientific outreach events, features in newspaper and magazine articles, and conducts radio interviews. He is a very naughty boy and was expelled from preschool\index{Montessori}.

@@

\dropcap{H}{e-Liang Huang} is a Postdoctoral Fellow at the University of Science \& Technology China (USTC). His research interests include secure cloud quantum computing, quantum big data analysis, and the physical implementation of quantum computing architectures, in particular using linear optical and superconducting systems. As an experimentalist he has been a part of several groundbreaking experimental efforts, most notably in the demonstration of world-leading multi-photon optical quantum information processing protocols. This includes the first experimental demonstration of topological data analysis on a photonic quantum computer, an optical demonstration of blind quantum computing, and a loophole-free Wheeler-delayed-choice experiment.

@@

\dropcap{Z}{u-En Su} is a PhD candidate at the University of Science \& Technology China.

@@

\dropcap{Z}{ixin Huang} completed her PhD in physics at the University of Sydney, Australia. She is currently a postdoctoral fellow at the University of Sheffield, UK.

@@

\dropcap{C}{handrashekar Radhakrishnan} is a Postdoctoral Fellow and Bright Overseas Global Corporation Scholar at New York University, Shanghai, Chibna. He is a recipient of the National Natural Science Foundation of China, International Young Scientist research grant. Before Joining NYU Shanghai he worked as a Postdoctoral Fellow at the Institute of Mathematical Science, India and the National Chung Hsing University, Taiwan. He obtained his Master of Science in Physics from the Indian Institute of Technology Madras and a PhD in theoretical physics from University of Madras. He has worked on a variety of fields, including statistical mechanics, mathematical physics and quantum information theory. His fundamental interest in quantum information theory lies in investigating quantum resources alternative to entanglement, which can be used for quantum communication and quantum computation. He has active collaborations with experimentalists, through which he tries to verify his theoretical results. He also has some interest in the application of statistical mechanics to biological problems.

@@

\comment{Complete}

\dropcap{S}{imon Devitt}

@@

\dropcap{S}{i-Hui Tan} is a Research Scientist at the Singapore University of Technology \& Design. She obtained a Bachelor of Science with Honours from Caltech, and subsequently a PhD from MIT. She has received numerous awards, including the MIT Presidential Fellowship.

@@

\dropcap{N}{ana Liu} is a Postdoctoral Research Fellow at the Singapore University of Technology \& Design.

@@

\dropcap{R}{ohit Ramakrishnan} is a researcher at the Indian Institute of Science.

@@

\dropcap{J}{on Dowling} is Professor and Hearne Chair of Theoretical Physics, and Co-Director of the Hearne Institute for Theoretical Physics at Louisiana State University. He has a highly-acclaimed research career, with over 450 publications and 15,000 citations. He is author of the popular book \textit{Schr\"odinger's Killer App: Race to Build the World's First Quantum Computer}.

@@

\dropcap{T}{im Byrnes}....

@@

\dropcap{B}{ill Munro} obtained his PhD at the University of Waikato, and has since held numerous prestigious fellowships and positions. He is currently Senior Research Scientist and leader of the theoretical quantum physics research group at NTT Japan.

### 2018-12-28 Sections/costs_and_attributes_in_quantum_networks.tex
indexing
Improved QM intro
Formatting update

In the special case of an identity channel, $\hat{\mathbb{I}}$, which is of special interest in many communications scenarios, we employ the shorthand,
\begin{align}
\mathcal{F}(\mathcal{E}) = \mathcal{F}(\mathcal{E},\hat{\mathbb{I}}) = \min_{\hat\rho} \left[\mathcal{F}(\hat\rho,\mathcal{E}(\hat\rho))\right].
\end{align}
By definition \mbox{$\mathcal{F}(\mathcal{E})=1$} iff \mbox{$\mathcal{E}=\hat{\mathbb{I}}$}.

@@

\subsubsection{Phase-space} \index{Phase-space!Errors}

@@

The Shannon entropy \cite{???} of a classical probability distribution $X$ is given by,
\begin{align}\index{Shannon entropy}
H(X) = -\sum_x p_x\log_2(p_x),
\end{align}
where $p_x$ are the probabilities in the distribution. For a joint distribution over $X$ and $Y$ this simply generalises to,
\begin{align}\index{Joint Shannon entropy}
H(X,Y) =  -\sum_{x,y} p_{x,y}\log_2(p_{x,y})
\end{align}

The von Neuman entropy \cite{???} for quantum density operators, $S(\hat\rho)$, is defined analogously, replacing probabilities with density operator eigenvalues,
\begin{align}\index{von Neuman entropy}
S(\hat\rho) &= - \sum_x \lambda_x \log_2 (\lambda_x) \nonumber \\
&= -\mathrm{tr}(\hat\rho\,\log \,\hat\rho),
\end{align}
where $\{\lambda\}$ is the eigenvalue spectrum of $\hat\rho$. This modification is logically justified, as the eigenvalues can be interpreted directly as a purely classical probability distribution of orthogonal states when the density operator is transformed into a basis with no coherences between basis states (i.e a diagonal basis or spectral decomposition). In that case the Shannon and von Neuman entropies essentially have identical physical interpretations.

@@

A dephasing channel can be easily converted to a distance metric as follows. First we reparameterise the dephasing channel into,
\begin{align}
\mathcal{E}(\hat\rho) &= p\hat\rho + (1-p)\hat{Z}\hat\rho\hat{Z}\nonumber\\
&= (2p-1)\hat\rho + (1-p)(\hat{Z}\hat\rho\hat{Z} + \hat\rho).	
\end{align}
Now \mbox{$2p-1$} is the probability that the state is not dephased and \mbox{$1-p$} is the probability that the state is replaced with the completely dephased state. Therefore the probability of multiple applications of the channel (\mbox{$\mathcal{E}_n\circ\dots\circ\mathcal{E}_1$}) not dephasing the state scales multiplicitavely as\footnote{With this parameterisation, in the limit of many applications of the dephasing channel, an input state asymptotes to the completely dephased state, \mbox{$\lim_{n\to\infty} \mathcal{E}^n(\hat\rho) = \frac{1}{2}(\hat{Z}\hat\rho\hat{Z}+\hat\rho)$}. Thus, \mbox{$2p-1$} can be regarded as a discretised parameterisation of a system's $T_2$-time\index{T$_2$-time}.},
\begin{align}
p_\mathrm{no\, error} = \prod_{i}(2p_i-1),
\end{align}
which is additive in a logarithmic scale as before,
\begin{align}
\log(p_\mathrm{no\, error}) = \sum_i \log(2p_i-1),
\end{align}
which acts as a distance metric. This approach can similarly be applied to other Pauli channels.

>>>>

In the special case of an identity channel, $\hat\openone$, which is of special interest in many communications scenarios, we employ the shorthand,
\begin{align}
\mathcal{F}(\mathcal{E}) = \mathcal{F}(\mathcal{E},\hat\openone) = \min_{\hat\rho} \left[\mathcal{F}(\hat\rho,\mathcal{E}(\hat\rho))\right].
\end{align}
By definition \mbox{$\mathcal{F}(\mathcal{E})=1$} iff \mbox{$\mathcal{E}=\hat\openone$}.

@@

\subsubsection{Phase-space} \index{Phase!Space!Errors}

@@

The Shannon entropy\index{Shannon entropy} \cite{???} of a classical probability distribution $X$ is given by,
\begin{align}\index{Shannon entropy}
H(X) = -\sum_x p_x\log_2(p_x),
\end{align}
where $p_x$ are the probabilities in the distribution. For a joint distribution over $X$ and $Y$ this simply generalises to,
\begin{align}\index{Joint Shannon entropy}
H(X,Y) =  -\sum_{x,y} p_{x,y}\log_2(p_{x,y})
\end{align}

The von Neuman entropy\index{von Neuman entropy} \cite{???} for quantum density operators, $S(\hat\rho)$, is defined analogously, replacing probabilities with density operator eigenvalues,
\begin{align}\index{von Neuman entropy}
S(\hat\rho) &= - \sum_x \lambda_x \log_2 (\lambda_x) \nonumber \\
&= -\mathrm{tr}(\hat\rho\,\log \,\hat\rho),
\end{align}
where $\{\lambda\}$ is the eigenvalue spectrum of $\hat\rho$. This modification is logically justified, as the eigenvalues can be interpreted directly as a purely classical probability distribution of orthogonal states when the density operator is transformed into a basis with no coherences between basis states (i.e a diagonal basis or spectral decomposition). In that case the Shannon and von Neuman entropies essentially have identical physical interpretations.

@@

A dephasing channel can be easily converted to a distance metric as follows. First we reparameterise the dephasing channel into,
\begin{align}
\mathcal{E}(\hat\rho) &= p\hat\rho + (1-p)\hat{Z}\hat\rho\hat{Z}\nonumber\\
&= (2p-1)\hat\rho + (1-p)(\hat{Z}\hat\rho\hat{Z} + \hat\rho).	
\end{align}
Now \mbox{$2p-1$} is the probability that the state is not dephased and \mbox{$1-p$} is the probability that the state is replaced with the completely dephased state. Therefore the probability of multiple applications of the channel (\mbox{$\mathcal{E}_n\circ\dots\circ\mathcal{E}_1$}) not dephasing the state scales multiplicatively as\footnote{With this parameterisation, in the limit of many applications of the dephasing channel, an input state asymptotes to the completely dephased state, \mbox{$\lim_{n\to\infty} \mathcal{E}^n(\hat\rho) = \frac{1}{2}(\hat{Z}\hat\rho\hat{Z}+\hat\rho)$}. Thus, \mbox{$2p-1$} can be regarded as a discretised parameterisation of a system's $T_2$-time\index{T$_2$-time}.},
\begin{align}
p_\mathrm{no\, error} = \prod_{i}(2p_i-1),
\end{align}
which is additive in a logarithmic scale as before,
\begin{align}
\log(p_\mathrm{no\, error}) = \sum_i \log(2p_i-1),
\end{align}
which acts as a distance metric. This approach can similarly be applied to other Pauli channels.

### 2018-12-28 Sections/cryptowars.tex
Formatting update

A downside of RSA is that ciphertexts are in general much longer than plaintexts, unlike private-key protocols where the ciphertext is always the same length as the plaintext. For this reason it is typically not used to directly encrypt long messages, since the memory and bandwidth overheads would be undesirable. Instead, RSA is typically employed in conjunction with private-key cryptography in a key exchange protocol\index{Key exchange protocol}. Here the public-key system communicates a private \textit{session key}\index{Session key} between parties, which is subsequently employed in a private-key protocol, without incurring the time and memory overhead that RSA does. In Sec.~\ref{sec:brute_force_attacks} we point out that quantum computers are not believed to be able to efficiently crack private-key protocols, but instead effectively reduce their key length by a factor of 1/2, which is easily counteracted with longer keys to restore security.

Numerous key exchange protocols have been formulated, the best known being the Diffie-Hellman\index{Diffie-Hellman protocol} protocol \cite{DiffieHellman}, which has been widely adopted on the internet.

@@

Hash functions have broad applicability throughout computer science, but here we are most interested in \textit{cryptographic hash functions} for use in cryptography, which impose strong conditions on the difficulty of inversion and their quasi-random characteristics. Most notably, the desired characteristics of a cryptographic hash function include:
\begin{itemize}
	\item The distribution of hashes ought not exhibit any biases, following a uniform distribution with quasi-random\index{Quasi-random} behaviour.
	\item Changing a single bit in the input string ought to flip approximately half the bits of the hash on average.	
	\item It's computationally efficient to calculate a hash from an input.
	\item It's computationally complex to find an input that hashes to a given value.
	\item The hashes of two very similar inputs ought to yield hashes that a very different.
	\item Two different inputs are extremely unlikely to hash to the same value.
\end{itemize}

@@

%
% Quantum Attackes
%

@@

Thankfully, there are two saving graces. First of all, much research is being carried out into \textit{post-quantum classical cryptography}\index{Post-quantum classical cryptography}. That is, public-key cryptosystems based upon trapdoor functions\index{One-way functions} that reside outside of \textbf{BQP} and are therefore not efficiently attacked by quantum computers. One such line of research is to construct cryptosystems based upon \textbf{NP}-complete problems, such as the McEliece protocol\index{McEliece protocol} \cite{bib:McEliece}. Recall from Fig.~\ref{fig:complexity_classes} that \textbf{NP}-complete is strongly believed to reside completely outside of \textbf{BQP}. However, while many computer scientists might be comfortable with such a level of security, it is nonetheless based on the unproven conjecture that \textbf{NP}-complete and \textbf{BQP} do not intersect, i.e \mbox{$\mathbf{NP}\nsubseteq\mathbf{BQP}$}. What would be much more satisfying would be protocols demonstrating information-theoretic security\index{Information-theoretic!Security} rather than computational security\index{Computational!Security}. Here quantum mechanics can help us -- \textit{quantum cryptography}.

@@

The central notion to QKD protocols, in their numerous manifestations, is that measurement of quantum states invokes a wavefunction collapse. When measuring a state in a basis for which that state is not an eigenstate, this necessarily changes the state. QKD relies on this simple result from quantum mechanics to reveal any eavesdropper performing an intercept-resend attack\index{Intercept-resend attacks} via the changes to transmitted quantum states that this would induce.

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{enigma_machines}
\captionspacefig \caption{Schematic of the quantum Enigma machine protocol for quantum private-key cryptography. $\ket{j}$ is the message, $k$ is the key, and $\hat{U}_k$ is the encryption operation associated with key $k$, chosen randomly from the Haar measure. The encrypted message is $\ket{j}_k$. An eavesdropper intercepting the channel without knowledge of the key observes the state $\hat\rho_\mathrm{enc}$.}\index{Quantum Enigma machines}\label{fig:enigma}	
\end{figure}

@@

A beamsplitting (BS) attack translates the fact that any signal lost over a channel is acquired by Eve. Here Eve induces losses in the communications channel by putting a beamsplitter outside Alice's device, then forwards the remaining photons to Bob. The BS attack does not modify the optical mode that Bob receives: it's therefore always possible for lossy channels, and does not introduce any errors.

@@

The faked-state attack\index{Faked-state attack} is based on the weak-laser implementation of BB84. Here Eve manipulates Bob's detectors to force him to measure in the same basis. It exploits the fact that the detectors may have a dead-time\index{Dead-time}, and the eavesdropper can trigger the detector whenever she chooses. It follows that Bob's detection outcomes are controlled by the eavesdropper.

>>>>

A downside of RSA is that ciphertexts are in general much longer than plaintexts, unlike private-key protocols where the ciphertext is always the same length as the plaintext. For this reason it is typically not used to directly encrypt long messages, since the memory and bandwidth overheads would be undesirable. Instead, RSA is typically employed in conjunction with private-key cryptography in a key exchange protocol\index{Key exchange protocol}. Here, the public-key system communicates a private \textit{session key}\index{Session key} between parties, which is subsequently employed in a private-key protocol, without incurring the time and memory overhead that RSA does. In Sec.~\ref{sec:brute_force_attacks} we point out that quantum computers are not believed to be able to efficiently crack private-key protocols, but instead effectively reduce their key length by a factor of 1/2, which is easily counteracted with longer keys to restore security.

Numerous key exchange protocols have been formulated, the best known being the Diffie-Hellman\index{Diffie-Hellman protocol} protocol \cite{bib:DiffieHellman}, which has been widely adopted on the internet.

@@

Hash functions have broad applicability throughout computer science, but here we are most interested in \textit{cryptographic hash functions} for use in cryptography, which impose strong conditions on the difficulty of inversion and their quasi-random characteristics. Most notably, the desired characteristics of a cryptographic hash function include:
\begin{itemize}
	\item The distribution of hashes ought not exhibit any biases, following a uniform distribution with quasi-random\index{Quasi-random} behaviour.
	\item Changing a single bit in the input string ought to flip approximately half the bits of the hash on average.	
	\item It's computationally efficient to calculate a hash from an input.
	\item It's computationally complex to find an input that hashes to a given value (that is, they are one-way or trapdoor functions).\index{Trapdoor functions}
	\item The hashes of two very similar inputs ought to yield hashes that a very different.
	\item Two different inputs are extremely unlikely to hash to the same value.
\end{itemize}

@@

%
% Quantum Attacks
%

@@

Thankfully, there are two saving graces. First of all, much research is being carried out into \textit{post-quantum classical cryptography}\index{Post-quantum classical cryptography}. That is, public-key cryptosystems based upon trapdoor functions\index{One-way functions} that reside outside of \textbf{BQP} and are therefore not efficiently attacked by quantum computers. One such line of research is to construct cryptosystems based upon \textbf{NP}-complete problems, such as the McEliece protocol\index{McEliece protocol} \cite{bib:McEliece}. Recall from Fig.~\ref{fig:complexity_classes} that \textbf{NP}-complete is strongly believed to reside completely outside of \textbf{BQP}. However, while many computer scientists might be comfortable with such a level of security, it is nonetheless based on the unproven conjecture that \textbf{NP}-complete and \textbf{BQP} do not intersect, i.e \mbox{$\mathbf{NP}\nsubseteq\mathbf{BQP}$}. What would be much more satisfying would be protocols demonstrating information-theoretic security\index{Information-theoretic!Security} rather than computational security\index{Computational!Security}. Here, quantum mechanics can help us -- \textit{quantum cryptography}.

@@

The central notion to QKD protocols, in their numerous manifestations, is that measurement of quantum states invokes a wave-function collapse. When measuring a state in a basis for which that state is not an eigenstate, this necessarily changes the state. QKD relies on this simple result from quantum mechanics to reveal any eavesdropper performing an intercept-resend attack\index{Intercept-resend attacks} via the changes to transmitted quantum states that this would induce.

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{enigma_machines}
\captionspacefig \caption{Schematic of the quantum Enigma machine protocol for quantum private-key cryptography. $\ket{j}$ is the message, $k$ is the key, and $\hat{U}_k$ is the encryption operation associated with key $k$, chosen randomly from the Haar measure\index{Haar measure}. The encrypted message is $\ket{j}_k$. An eavesdropper intercepting the channel without knowledge of the key observes the state $\hat\rho_\mathrm{enc}$.}\index{Quantum Enigma machines}\label{fig:enigma}	
\end{figure}

@@

A beamsplitting (BS) attack translates the fact that any signal lost over a channel is acquired by Eve. Here, Eve induces losses in the communications channel by putting a beamsplitter outside Alice's device, then forwards the remaining photons to Bob. The BS attack does not modify the optical mode that Bob receives: it's therefore always possible for lossy channels, and does not introduce any errors.

@@

The faked-state attack\index{Faked-state attack} is based on the weak-laser implementation of BB84. Here, Eve manipulates Bob's detectors to force him to measure in the same basis. It exploits the fact that the detectors may have a dead-time\index{Dead-time}, and the eavesdropper can trigger the detector whenever she chooses. It follows that Bob's detection outcomes are controlled by the eavesdropper.

### 2018-12-28 Sections/economics_of_the_quantum_internet.tex
Formatting update

\begin{postulate}[Efficient markets]\label{post:market_eff}\index{Efficient markets} We make the following efficiency assumptions on the dynamics of the quantum marketplace:
\begin{itemize}
	\item Qubits are a `scarce' resource --- there is always positive, non-zero demand for them.\index{Scarcity}
	\item No wastage --- quantum computational resources are always fully utilised, with no down-time.\index{Wastage}
	\item Transaction free --- transaction costs are negligible, for both quantum assets and their derivatives.\index{Transaction cost}
	\item Negligible cost-of-carry --- e.g storage and maintenance costs are negligible.\index{Cost of carry}
	\item High liquidity --- it is always possible to execute transactions at market rates.\index{Liquidity}
	\item Perfect competition --- there are no monopolies gouging prices, which are in equilibrium.\index{Perfect competition}
	\item Arbitrage-free --- market rates for different assets and derivatives are perfectly consistent, with no opportunity for `free money' by trading on market discrepancies.\index{Arbitrage-free}
	\item Perfect information --- all market participants have complete knowledge of all market variables, including one another.\index{Perfect information}
	\item Rational markets --- all market participants act rationally\footnote{i.e with perfect economic self-interest \latinquote{Avaritia}.} upon available information.\index{Rational markets}
	\item Indefinite asset lifetime --- there is no deterioration or death of quantum hardware over time.\index{Asset lifetime}
	\item There is a risk-free rate of return ($r_\mathrm{rf}$)\index{Risk-free!Rate of return}
-- the rate of growth exhibited by an investment into an optimal risk-free asset\footnote{Historically these risk-free assets are taken as being US government bonds\index{US government bonds}\index{Risk-free!Asset}, with the bond yield being the risk-free RoR.}
	\end{itemize}
\end{postulate}

@@

This observation motivates us to re-parameterise the power of quantum computers in terms of the problem size of a given algorithm to be solved. Employing the same methodology as for computational scaling functions, we define the \textit{problem size scaling function}, which relates the size of an algorithmic problem to it's classical equivalent runtime. Then equating the computational and problem size scaling function yields,

>>>>

\begin{postulate}[Efficient markets]\label{post:market_eff}\index{Efficient markets} We make the following efficiency assumptions on the dynamics of the quantum marketplace:
\begin{itemize}
	\item Qubits are a `scarce' resource: there is always positive, non-zero demand for them.\index{Scarcity}
	\item No wastage: quantum computational resources are always fully utilised, with no down-time.\index{Wastage}
	\item Transaction free: transaction costs are negligible, for both quantum assets and their derivatives.\index{Transaction cost}
	\item Negligible cost-of-carry: e.g storage and maintenance costs are negligible.\index{Cost of carry}
	\item High liquidity: it is always possible to execute transactions at market rates.\index{Liquidity}
	\item Perfect competition: there are no monopolies gouging prices, which are in equilibrium.\index{Perfect competition}
	\item Arbitrage-free: market rates for different assets and derivatives are perfectly consistent, with no opportunity for `free money' by trading on market discrepancies.\index{Arbitrage-free}
	\item Perfect information: all market participants have complete knowledge of all market variables, including one another.\index{Perfect information}
	\item Rational markets: all market participants act rationally\footnote{i.e with perfect economic self-interest \latinquote{Avaritia}.} upon available information.\index{Rational markets}
	\item Indefinite asset lifetime: there is no deterioration or death of quantum hardware over time.\index{Asset lifetime}
	\item There is a risk-free rate of return ($r_\mathrm{rf}$)\index{Risk-free!Rate of return}: the rate of growth exhibited by an investment into an optimal risk-free asset\footnote{Historically these risk-free assets are taken as being US government bonds\index{US government bonds}\index{Risk-free!Asset}, with the bond yield being the risk-free RoR.}
	\end{itemize}
\end{postulate}

@@

This observation motivates us to re-parameterise the power of quantum computers in terms of the problem size of a given algorithm to be solved. Employing the same methodology as for computational scaling functions, we define the \textit{problem size scaling function}, which relates the size of an algorithmic problem to its classical equivalent runtime. Then equating the computational and problem size scaling function yields,
